%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% Adjust margins for balanced spacing on all sides
\usepackage[letterpaper, left=0.7in, right=0.7in, top=0.8in, bottom=0.8in]{geometry}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
  \textbf{\Huge \scshape Manan Uppadhyay} \\ \vspace{1pt}
  \small +91 7650876355 $|$ \href{mailto:mananuppadhyay@gmail.com}{\underline{mananuppadhyay@gmail.com}} $|$
  \href{https://github.com/mananuppadhyay}{\underline{https://github.com/mananuppadhyay}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Birla Institute of Technology and Science, Pilani} {Goa}
  {B.E. Electrical and Electronics Engineering}{2020-2024}
  \newline
  \resumeItemListStart
  \resumeItemListEnd

\resumeSubheading
  {Birla Institute of Technology and Science, Pilani} {Goa}
  {Minor Degree in Data Science}{2022-2024}
  \newline
  \resumeItemListStart
  \resumeItemListEnd

\resumeSubheading
  {Stepping Stones Sr. Secondary School} {Chandigarh}
  {Schooling}{2018-2020}
\newline
\resumeItemListStart
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------COURSEWORK-----------
\section{Coursework}
\resumeSubHeadingListStart
\resumeItem{
  \textbf{Math}{: Probability and Statistics, Statistical Inference and Applications, Applied Stochastic processes, Applied Statistical Methods, Optimization, Linear Algebra}
}
\resumeItem{
  \textbf{Machine/Deep Learning}{: Machine Learning, Foundations of Data Science, Large Language Models (In association with TCS Research), Digital Image Processing}
}
\resumeSubHeadingListEnd


\section{Publications}
\resumeSubHeadingListStart

\resumeProjectHeading
   {{\small \textbf{The Role of Synthetic Data in Multilingual, Multicultural AI Systems: Lessons from Indic Languages}}} {}
  \resumeItemListStart
    \resumeItem{\small{Developed \textbf{UPDESH}, a 9.5 million-sample culturally grounded synthetic instruction dataset across 13 Indic languages to narrow performance gaps in multilingual AI.}}
    \resumeItem{\small{Accepted at \textbf{ACL 2026 (Main track)}. Preprint: \href{https://arxiv.org/abs/2509.21294}{arXiv:2509.21294}.}}
  \resumeItemListEnd

\resumeProjectHeading
  {{\small\textbf{Garuda: An Indian Agricultural LLM and Krishi Saathi Advisory Chatbot}}} {}
  \resumeItemListStart
    \resumeItem{\small{Accepted as a hands-on demonstration paper at the Workshop on Open-Source AI for Mainstream Use at \textbf{AAAI 2025}.}}
  \resumeItemListEnd

\resumeSubHeadingListEnd



% -------------------- EXPERIENCE --------------------
\section{Experience}
\resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{Research Fellow} \hfill \textbf{Microsoft Research}} {August 2025 -- Present}
  \resumeItemListStart

  \resumeItem{Worked on \textbf{Updesh}, a 9.5 million-sample culturally grounded synthetic instruction dataset, fine-tuning models on the same and performing downstream evaluations.}
  \resumeItem{Working on \textbf{Samiksha}: A large scale multilingual evaluation suite for LLMs, with a focus on improving and adapting LLMs as judges to an Indian multilingual-multicultural domain. s}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Data Scientist} \hfill \textbf{Razorpay}} {Apr 2025 -- Aug 2025}
  \resumeItemListStart
    \resumeItem{\small{Converted the existing payment routing system (\textbf{Doppler}) from classical ML to a real-time \textbf{multi-armed bandit reinforcement learning} framework to optimize transaction success rates.}}
    \resumeItem{\small{Designed and deployed \textbf{Airflow DAGs} for automated data retrieval and performance evaluation of routing systems.}}
    \resumeItem{\small{Conducted extensive \textbf{EDA} and rebuilt feature engineering pipelines to retrain classical models, improving daily payment success rate by \textbf{2\%}.}}
  \resumeItemListEnd


\resumeProjectHeading
  {\textbf{Associate ML Scientist-1} \hfill \textbf{Wadhwani AI}} {August 2024 -- March 2025}
  \resumeItemListStart
  \resumeItem{Developed a domain-specific language model for agriculture, utilizing fine-tuning techniques and synthetic data pipelines to improve performance, achieving a \textbf{1-5\% improvement over GPT-4o-mini} on key internal benchmarks.}

  \resumeItem{Designed and deployed a chatbot for Kisan Call Centres (KCC), using an agentic LLM workflow to assist the advisors in quick query resolution for the farmers. The chatbot served \textbf{3,000 queries daily} during pilot runs across 11 states, with plans to scale further.}
  \resumeItem{Worked closely with the Kisan eMitra Chatbot, streamlining insurance related grievance resolution, covering \textbf{3 government schemes and supporting over 3 million queries in 8 months}, benefiting \textbf{250,000+ farmers}.}
  \resumeItemListEnd



\resumeProjectHeading
  {\textbf{Machine Learning Intern} \hfill \textbf{Wadhwani AI}} {January 2024 -- July 2024}
  \resumeItemListStart
  \resumeItem{Implemented and compared Retrieval-Augmented Generation (RAG) and fine-tuning methods on models like Mistral-7B and LLaMA-8B for domain-specific downstream tasks.}
  \resumeItem{Designed and evaluated synthetic data pipelines for instruction tuning, enabling efficient model training.}
  \resumeItem{Evaluated and worked on improving LLM-generated responses in RAG-based setups to ensure high-quality performance and relevance.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Undergraduate Researcher} \hfill \textbf{APPCAIR, UNSW}} {August 2023 -- January 2024}
  \resumeItemListStart
  \resumeItem{Worked on building a 7 Million parameter deep learning model for detecting objects in endoscopic medical footage, deployable on edge devices.}
  \resumeItem{Implemented MobileOne architecture as the backbone with a detector on top, achieving \textbf{91\% mAP@50} in bounding box detection on endoscopic datasets.}
  \resumeItem{Supervised by: Prof. Tanmay Verlekar, Prof. Ashwin Srinivasan, Prof. Eric Meijering, Prof. Manik Gupta.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Summer Research Intern} \hfill \textbf{CSIR-CSIO, Chandigarh}} {May 2022 -- July 2022}
  \resumeItemListStart
  \resumeItem{Collaborated with a team of scientists on a data-driven project focused on water quality monitoring.}
  \resumeItem{Developed a dashboard to showcase contemporary research in water quality monitoring and testing.}
  \resumeItem{Applied regression algorithms to predict future water quality levels of Sukhna Lake, leveraging historical data for forecasting.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects and initiatives}

\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Cross Tokenizer Distillation}} {March 2025}
  \resumeItemListStart
  \resumeItem{Implemented the paper on Cross Tokenizer Distillation [ULD Loss] to enhance small-scale models by leveraging larger models as supervisors. \href{https://arxiv.org/pdf/2402.12030}{\textbf{(Paper)}}}
  \resumeItem{Trained bloomz-560m (student) using phi-3-mini-instruct (teacher) on the QED dataset, improving F1 score from \textbf{0.550 to 0.588}. \href{https://github.com/mananuppadhyay/cross-tokenizer-distillation}{\textbf{(GitHub code)}}}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{An implementation of Einops}} {April 2025}
  \resumeItemListStart
  \resumeItem{Implemented the einops library often used for tensor manipulations in plain numpy to supprot all rearrange and axis change operations \href{https://einops.rocks/}{\textbf{(The library)}}}
  \resumeItem{The code and the sample test cases generated for the same could be found in the \href{https://github.com/mananuppadhyay/einops_implementation}{\textbf{(GitHub code)}}}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Object detection using Res-YoLo}} {}
  \resumeItemListStart

  \resumeItem{Applied the model architecture taken from the \href{https://www.sciencedirect.com/science/article/pii/S0031320318302000}{\underline{paper}}, onto an open source car detection Dataset.}

  \resumeItem{Uses a ResNet backbone as a feature Extracter, and uses a YoLo like architecture to detect cars.}
  \resumeItem{Fine-Tuned the architecture on a car detection dataset, by freezing the intial few ResNet layers and training the custom detector in a regression like fashion.}
  \resumeItem{Tech stack: Pytorch, numpy, matplotlib \href{https://github.com/mananuppadhyay/ResYOLO}{\textbf{(The code)}}}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Identifying structural changes in an image} \hfill \textbf{Course Project for Machine Learning (BITS F464)}} {}
  \resumeItemListStart

  \resumeItem{Worked with a reasoning corpus similar to the ARC challenge with images with 2 pixel values and certain logical operations being performed on them.}
  \resumeItem{Experimented with models to classify the order of operations being performed after 8 operations at each step using Decison Trees and gradient boosting (XGBoost).}

  \resumeItem{TechStack: Python, numPy, pandas, scikit-learn, skimage \href{https://github.com/mananuppadhyay/ResYOLO}{\textbf{(The code)}}}

  \resumeItemListEnd

\resumeSubHeadingListEnd




%-----------COMMUNITY AND LEADERSHIP-----------
\section{Community and Leadership}

\resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{Debate Head} \hfill \textbf{The Literary and Debating Club BITS Goa}} {}
  \resumeItemListStart
  \resumeItem{Was responsible for leading the debating wing of the college club and training the members to participate in multiple debating competitions.}
  \resumeItem{Participated in multiple National and international Debating competitions as a speaker and a judge}
  \resumeItem{Some Notable Achievements: Runners up at MSRMPD, and open semifinalist at IITB,IITK,BITS Pilani debate tournaments. Judged the elimination rounds at Imperial IV and Leiden Open 2022}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}

\begin{itemize}[label={}]
  \small{
    \item \textbf{Languages}{: Python, C++, Java, C} \\* % Add "*\" for spacing after Languages line
    \item \textbf{Developer Tools}{: Git, Github, VS Code} \\*
    \item \textbf{Frameworks}{: Pytorch, TensorFlow, HuggingFace, Langchain, Llama Index, RAGAs} \\*
    \item \textbf{Libraries}{: numpy, pandas, scikit-learn, matplotlib, d3.js, dc.js} \\*
    \item \textbf{Applications}{: Autocad, Excel, Anaconda} \\*
    \item \textbf{Communication}{: English, Hindi}
  }
\end{itemize}



%-----------RESEARCH INTERESTS-----------
\section{Research interests}

\resumeSubHeadingListStart
\resumeItem{{\textbf{Large Language Models}{: Parameter efficient fine-tuning approaches, Evaluating LM responses and domain specific applications of LLMs, Retrieval Augmented Generation}}}
\resumeItem{\textbf{Computer Vision}{: Diffusion models, Vision Transformers for detection and segmentation}}
\resumeItem{\textbf{Theoretical ML}{: Stochastic modelling, Bayesian Modelling for Machine Learning}}
\resumeSubHeadingListEnd






%-------------------------------------------
\end{document}